The language of generalization: Probability, vagueness, and interaction

### 2018-10-18 paper/response.tex

\begin{letter}

\opening{Dear Professor Saxe,}

Thank you for soliciting peer reviews for our manuscript \emph{The Language of Generalization}. We appreciate the time both you and the reviewers have devoted to commenting and critiquing our manuscript. We are grateful for the opportunity to resubmit a revised version to be considered for publication in \emph{Psychological Review}.
We have made a number of substantive changes in this version of the manuscript that we hope will improve the readability of the paper.

Inspired by Reviewer 1's request to see the presentation of the various puzzles in a more accessible form,
we have merged the General Discussion subsection ``Other philosophical puzzles'' with the worked examples (e.g., \emph{birds lay eggs vs. are female}, \emph{mosquitos carry malaria}) that appeared before the experiments; now, both appear before the experiments.
We describe why each example is interesting, how the model handles each case, and provide a summary in a table (per R1's suggestion).
\textbf{We elaborated the puzzle of ``Elephants live in Africa and Asia'' by adding a figure of the model predictions for this example.
We note in the worked examples when the relevant puzzle will be tested empirically (e.g., we now foreshadow the relevance of \emph{predictive probability} and motivate Expt. 2C using ``Supreme Court Justices have even social security numbers'').}

We have taken Reviewers 1 and 3's suggestion of reconfiguring some of the general discussion material so now a comparison to other theories appears before the experiments (after the model section and worked examples).
We have also tightened this discussion, hopefully addressing R3's uncertainty about the relationship of our theories to extant theories. 
Our theory is, in R3's option-space, either (e) an outright alternative to prior theories, or (d) a more precise specification of (at least some aspects of) prior theories, namely Cohen (1999)'s domain-restriction theory and Leslie (2007)'s cognitively-based context sensitivity.
This equivocation comes because these previous theories admit different interpretations, only some of which are compatible with our model.
This is hopefully now more clearly articulated.

In the hope of addressing Reviewer 3's second comment, we include an additional subsection in the ``alternative theories'' section describing the various alternative quantitative models we will use for model comparison. 
The importance of these quantitative comparisons is slightly orthogonal to the comparisons to Leslie, Cohen, and other linguistic theories: These quantitative comparisons provide assurance that our model is not overparameterized and that the prior in our model is not doing all of the work. 
This also allows us to clarify the sense in which our model is unique (R3's third comment): It is the first model of generics that makes quantitative predictions about human endorsements (and it does so by connecting with a truth-conditional semantic theory in a particular way).

\textbf{Reviewer 3 also made the more general comment that the presentation of material meanders in the paper. 
We agree and have added a brief ``Intermediate summary'' section between the two halves of the paper (i.e., the model and related theories section vs. the experiments). 
This section summarizes the model, worked examples, and related theories and provides an overview of the experiments and the utility of each.
We hope this aids the readability.}

We tremendously appreciate Reviewer 2's thoughtful exposition on our account and have incorporated a number of their insights and suggestions into the General Discussion.
We have added a paragraph to the introductory remarks of the General Discussion about how accepting a generic sentence adds to the common ground information about cue validity, which suggests other empirical tests of the accounts.
We have noted as R2 does that there have been no empirical tests of the analogy between habituality and genericity, and that our formal machinery shows the way in which the two can be thought of as the same kind of linguistic phenomena.
We have added a subsection to the General Discussion to clarify the kind of vagueness we have in mind for generics, namely what R2 had in mind: vagueness and genericity are analogous linguistic phenomena insofar as they can both be thought of as the result of a listener being uncertainty as to the exact truth conditions. 
We note that, from a modeling perspective, this sort of ``lexical uncertainty`` is kind of \emph{parameter learning} problem (e.g., the listener knows the form of the truth conditions, but not the values of some variables) which can be formally distinguished from other sorts of uncertain truth conditions better modeled as a \emph{structure learning} problem (e.g., lexical ambiguity), \textbf{which might point the way towards a more general information-theoretic typology of underspecification. }
We clarify that the confluence of underlying mechanisms between generic vagueness and adjectival vagueness doesn't imply that generic vagueness has all the features of the adjectival kind (which indeed it probably doesn't -- for instance sorites sequences).
We additionally now discuss one interpretation of the uncertain threshold, drawing a connection explicitly to Williamson and Simons (1992)'s epistemicist view.\footnote{
	R2 actually cited Williamson (1994). In our literature search, however, we could only find a 1998 book chapter published in the Encyclopedia of Cognitive Science, a book published in 2002, both under the title ``Vagueness'', and a paper in 1992 called ``Vagueness and Ignorance'' written with Peter Simons. 
}

In addition to these broad theoretical points, we have tried to clarify a number of smaller points brought up by Reviewer 1.
We have been more explicit in our relation of generics with quantifiers as being from a purely semantic perspective, not taking into account pragmatic interpretations
We have removed our argument from analogy about states of uncertainty being more fundamental than states of certainty.
That comment was meant in a very particular way relating to Leslie (2007; 2008)'s theory and rhetoric; we now express the same idea by noting that our uncertain threshold model can be viewed as a formalization of Leslie's notion of a \emph{default generalization}. 
We have maintained our discussion of the acquisition of the semantics of generics because it has been a topic of interest to developmental psychologists (and central to Leslie's account), but we have cleaned up the prose and made explicit the way in which we believe learning generic language facilitates learning quantified semantics (in short: they share the same logical form, but the semantics of generics are simpler because they lack a fixed threshold).
\textbf{Reviewer 1 also brings to our attention property-based theories of concepts. We now note that we are not committed to any particular theory of concepts as long as they are able to generate quantitative feature probabilities (which could be brought about a number of different conceptual representations).  
We are now more explicit about this when discussing the role of conceptual knowledge in the General Discussion. }

@@

Finally we have gone through the manuscript and tried to make small changes to improve clarity and citations.

%things i'm not sure about:
%\begin{enumerate}
%\item property theories of meaning (R1) \ndg{they are alluding to theories of concepts -- conceptual role, feature-based, etc. i think we can add a few comments to the section on relation to conceptual theories of generics about this. basically we are not committed to any particular theory of concepts, as long as they are able to yield quantitative feature probabilities.} \mht{i didn't feel completely confident writing about theories of concepts and don't have a sense of ``standard`` citations that would convey succinctly our point. can you add this?}
%\end{enumerate}

### 2018-10-19 analysis/model-simulations.Rmd
clean up elephants and causal task figures; final polish on case study 3

fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 2, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('prevalence priors')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("")+
  ylab("Probability density")

fig.eleph.1 <- get_samples(rs.asia.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('"Elephants live in Africa..."')+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("Prevalence")+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 10000) %>%
  ggplot(., aes(x = state))+
  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  scale_x_continuous(limits = c(0, 1), breaks = c(0, 1))+
  xlab("")+
  ggtitle('"...and Asia"')+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

@@

>>>>

fig.eleph.0 <- get_samples(rs.asiaafrica.priors, 50000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 2, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('prevalence priors')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("")+
  ylab("Probability density")

fig.eleph.1 <- get_samples(rs.asia.marignals, 50000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('"Elephants live in Africa..."')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("Prevalence")+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

fig.eleph.2 <- get_samples(rs.asiaafrica.marignals, 50000) %>%
  ggplot(., aes(aes(y = ..scaled..),x = state))+
  geom_density(adjust = 4, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("")+
  ggtitle('"...and Asia"')+
  ylab("Probability density")+
  theme(axis.title.y = element_blank())

@@

```{r}
get_samples(rs.asiaafrica.priors, 50000) %>%
  ggplot(., aes(x = state))+
  geom_density(aes(y = ..scaled..),adjust = 2, fill = 'grey', alpha = 0.3)+
  facet_wrap(~marginal, ncol = 1)+
  ggtitle('prevalence priors')+
  scale_x_continuous(limits = c(-0.05, 1.05), breaks = c(0, 1))+
  xlab("")+
  ylab("Probability density")
```

### 2018-10-19 paper/case3-causals.Rmd
clean up elephants and causal task figures; final polish on case study 3

In this experiment, we manipulate participants' background knowledge, measuring these beliefs in order to check whether the manipulation was successful. 
Experiment 3b (*causal endorsement*) will then use a very similar experimental procedure in exploring causal generalization language.

@@

Participants were told a story of a scientific experiment testing different substances to produce an effect (either to make animals sleepy or make plants grow tall). 
Our cover stories were constructed so that the potential cause could have some plausible intuitive mechanism that could give rise to the property (e.g., a naturally occurring herb causing animals to be sleepy). 
The two cover stories can be seen in Table 2.

Participants were then shown "previous experimental results", which followed one of four distributions.
In two of the conditions, participants saw results that came from a single underlying distribution (*common* conditions).
In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the *common strong* condition).
In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the *common weak* condition).
<!-- The results of the previous experiments were described verbally  -->
<!-- These distributions had the feeling that either there was some background cause which gave rise to the effect (e.g., a simple base rate) or that all substances were equally as efficacious at producing the effect. -->
The two other conditions used distributions in which some experiments resulted in either no or very few successes (i.e., produced 0, 1, or 2 successes), and others that either had strong or weak effects as above. 
These are the *rare strong* and *rare weak* conditions.
<!-- These distributions had the feeling that the effect was somewhat rare and that only certain substances produced any effect. -->

@@

```{r causalExpt, fig.cap="Overview of Experiment 3. A-C: Results of previous experiments are shown one at a time, described in text and displayed in a table. One of the results was lost. Participants are asked to review previous results once all displayed. D: Prior elicitation task: Participants predict the results of the next 5 experiments. E: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, out.width = "\\textwidth", fig.pos = "!h", cache=F}
caus.exp.1 <- ggdraw() + draw_image("figs/causal-expt-1.jpeg", scale = 1) +
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.2 <- ggdraw() + draw_image("figs/causal-expt-2.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.3 <- ggdraw() + draw_image("figs/causal-expt-3.jpeg", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.4 <- ggdraw() + draw_image("figs/causal-expt-prior.jpeg", scale = 1)
caus.exp.5 <- ggdraw() + draw_image("figs/causal-expt-endorse.jpeg", scale = 1)

caus.exp.toprow <- plot_grid(caus.exp.1, caus.exp.2, caus.exp.3, labels = c("A", "B", "C"), nrow = 1, align = 'vh')

title <- ggdraw() + draw_label("Prevalence prior manipulation")
plot_grid(
  plot_grid(title, caus.exp.toprow, ncol=1, rel_heights=c(0.1, 1)),
  plot_grid(add_sub(caus.exp.4, "Prior elicitation"), add_sub(caus.exp.5,"Causal endorsement"), labels = c("D", "E"), nrow = 1),
  nrow = 2)
```

@@

Participants then click a button to show the results of the experiments.
Experiment results appear one at a time (upon a click), and are described in an *evidence statement* (e.g., "Your team gave herb A to 100 different cheebas. Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes (e.g., "animals made sleepy") per number of attempts (always 100 per experiment; Figure \@ref(fig:causalExpt)A). 
We described the results of these individual experiments using token-level causal language (e.g., "98 cheebas were made sleepy") to imply that actual causation occurred in these cases.

Participants see the results of eleven experiments, though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)B). 
(These lost results would be found in the *causal endorsement* task, Expt. 3b).
After participants viewed the results of the 10 "experiments" (and 1 missing experiment), they are told to review the results of the experiments before continuing (Figure \@ref(fig:causalExpt)C).

Upon clicking the continue button, the table of experiment results is removed and participants are told more experiments were conducted.
Participants were asked to predict the results of the next 5 experiments (Figure \@ref(fig:causalExpt)D).
Participants were given five slider bars ranging from 0 - 100, and asked to predict the next five substances (e.g., herbs M, N, P, Q, and R).

After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigating (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen. 
This attention check served to confirm that participants had encoded both relevant aspects of the experiment (the domain and the frequencies).

@@

`r n.subj.cas.failed` participants were excluded from the analysis for failing to answer both of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
The empirically elicited distributions of responses were not appreciably different for our two cover stories (herbs making animals sleepy, fertilizer making plants grow tall) and thus we collapse the data across these two stories.
The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure\ \@ref(fig:figure-causals)A.
<!-- \ndg{its unclear in figure caption whether those are emprical, predicted, or bda priors.} -->
As is visually apparent, the empirical prevalence distributions differ between conditions and nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition. 
This diversity is important because the model of generalizations predicts differences in endorsement---for the same referent prevalence---depending on these priors.
<!-- \ndg{it'd be good to have some kid of stats here. maybe just show that empirical prealence distributions differ between conditions. also say how this matters: as before geeralization model predicts differences in endorsement for same target prevalence depending on priors.} -->
<!-- We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected. -->

@@

In this experiment, we tested whether the manipulated priors of Expt. 3a are causally related to the endorsement of causal statements.
Most of the experimental design was identical to that of Experiment 3a.

@@

The materials were the same as in Expt. 3a.
The first part of the experimental trial was the same as in Expt. 3a (the table of "previous experiments"; Figure \@ref(fig:causalExpt)A-C).
Upon continuing beyond the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found. 
The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
Participants saw one of two reported frequencies: 20\% or 70\% (randomized between-subjects).
Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy") by either clicking "Yes" or "No" (Figure \@ref(fig:causalExpt)E). 
This allows us to test whether endorsement of a causal sentence for a given actual frequency is affected by the causal priors induced by our manipulation.
After responding, participants completed the same attention check as Expt. 3a.

@@

As predicted by our model, endorsements for a causal statement were sensitive to the causal power of the target cause and, critically, to the background distribution of other causes. 
When many other causes produced the effect very reliably (*common strong* condition), very few participants endorsed the causal statement for a cause with causal power of 0.2, and were at chance when the causal power was 0.7 (Figure\ \@ref(fig:figure-causals)A).
By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal power of 0.2, and were at ceiling when the causal power was 0.7.
The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
These effects were predicted by our model with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).

@@

In our third case study, we applied our model to generalizations about causal events, without any changes.
In this domain, we successfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3a).
This was done using both unimodal (*common weak*, *common strong*) and bimodal (*rare weak*, *rare strong*) distributions. 
In Expt. 3b, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
In addition to further demonstrating the generality of this theory, these experiments show that the prevalence prior $P(p)$ is causally related to endorsements of generalizations in language.
<!-- To our knowledge, these are the first experiments to demonstrate how the prevalence of a feature among other categories can influence endorsing a generalization about a referent category. \ndg{fix last sentence. is this about geeralization? didn't our last experiments show this? is it about causation? huh?} -->

In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall.
<!-- \ndg{which reminds me: need to say something above (3a) about (no) differences between the cover stories?} -->
We chose these items because there was a plausible causal mechanism that could give rise to the property and these causal events could have ambiguous causal power associated with them (e.g., it is plausible that there are herbs that only weakly make animals sleepy and it is also plausible that there are herbs that almost deterministically make animals sleepy).
These two features of the domains make them particularly amenable to manipulation.
<!-- Inituive theories about these domains are flexible enough to permit such manipulations. -->

It is likely that other domain knowledge would interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
If this were happening in our domains, we would expect this to show up in the results of Expt. 3a. Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
]
For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causal power, analogous to our *strong* priors conditions. 
Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analogous to our *rare* prior conditions. 
Our theory would predict that differences in endorsement in these cases would be mediated by differences in the corresponding prevalence prior distributions.

>>>>

In this experiment, we manipulate participants' background knowledge, measuring these beliefs in order to check whether the manipulation was successful. 
Experiment 3B (*causal endorsement*) will then use a very similar experimental procedure in exploring causal generalization language.

@@

Participants were told a story of a scientific experiment testing different substances to produce an effect (either to make animals sleepy or make plants grow tall). 
Our cover stories were constructed so that the potential cause could have some plausible intuitive mechanism that could give rise to the property (e.g., a naturally occurring herb causing animals to be sleepy). 
The two cover stories can be seen in Table 3.

Participants were then shown "previous experimental results", which followed one of four distributions represented as a table of numbers.
In two of the conditions, participants saw results that came from a single underlying distribution (*common* conditions).
In one of these conditions, all causes produced a strong effect (average efficacy approximately 98\%; the *common strong* condition).
In the second of these conditions, all causes produced a weak effect (average efficacy approximately 20\%; the *common weak* condition).
<!-- The results of the previous experiments were described verbally  -->
<!-- These distributions had the feeling that either there was some background cause which gave rise to the effect (e.g., a simple base rate) or that all substances were equally as efficacious at producing the effect. -->
The two other conditions used distributions in which some experiments resulted in either no or very few successes (i.e., produced 0, 1, or 2 successes), and others that either had strong or weak effects as above. 
These are the *rare strong* and *rare weak* distributions.
<!-- These distributions had the feeling that the effect was somewhat rare and that only certain substances produced any effect. -->

@@

```{r causalExpt, fig.cap="Overview of Experiment 3. A-C: Results of previous experiments are shown one at a time, described in text and displayed in a table. One of the results was lost. Participants are asked to review previous results once all displayed. D: Prior elicitation task: Participants predict the results of the next 5 experiments. E: Causal endorsement task: Results of previously lost experiment are found and participants are asked to evaluate the causal generalization.", fig.width = 10, out.width = "\\textwidth", fig.pos = "!h", cache=F}
caus.exp.1 <- ggdraw() + draw_image("figs/causal-task/causal-task.001.png", scale = 1) +
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.2 <- ggdraw() + draw_image("figs/causal-task/causal-task.002.png", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.3 <- ggdraw() + draw_image("figs/causal-task/causal-task.003.png", scale = 1)+
  theme(plot.margin = unit(c(2,0,0,0), "pt")) 
caus.exp.4 <- ggdraw() + draw_image("figs/causal-task/causal-task.004.png", scale = 1)
caus.exp.5 <- ggdraw() + draw_image("figs/causal-task/causal-task.005.png", scale = 1)

caus.exp.toprow <- plot_grid(caus.exp.1, caus.exp.2, caus.exp.3, labels = c("A", "B", "C"), nrow = 1, align = 'vh', rel_widths = c(1, 1.2, 2))

title <- ggdraw() + draw_label("Prevalence prior manipulation")
plot_grid(
  plot_grid(title, caus.exp.toprow, ncol=1, rel_heights=c(0.1, 1)),
  plot_grid(caus.exp.4,caus.exp.5, labels = c("D", "E"), nrow = 1, align = 'v'),
  nrow = 2)
```

@@

Participants then clicked a button to show the results of the experiments, which appeared one at a time in a random order (following a particular distribution).
Experimental results were also are described in an *evidence statement* (e.g., "Your team gave herb A to 100 different cheebas. Of those 100 treated, 98 cheebas were made sleepy.") as well as displayed in a table showing the number of successes (e.g., "animals made sleepy") per number of attempts (always 100 per experiment; Figure \@ref(fig:causalExpt)A). 
We described the results of these individual experiments using token-level causal language (e.g., "98 cheebas were made sleepy") to imply that actual causation occurred in these cases.
Participants see the results of eleven experiments, though they are told the results of one experiment were lost and a "?" was placed in the table (Figure \@ref(fig:causalExpt)B). 
(These lost results would be found in the *causal endorsement* task, Expt. 3B).
After participants viewed the results of the 10 experiments (and 1 missing experiment), they are told to review the results of the experiments before continuing (Figure \@ref(fig:causalExpt)C).

Upon clicking the continue button, the table of experiment results is removed and participants are told that five more experiments were conducted that day and asked to predict the results of those experiments (Figure \@ref(fig:causalExpt)D).
Participants were given five slider bars ranging from 0 - 100 to rate the number of predicted successes out of 100 attempts.
After responding, participants then completed an attention check survey where they were asked what the team of scientists were investigating (choosing a response from a drop-down menu with 12 options) and to input one of the numerical results they saw on the previous screen. 
This attention check served to confirm that participants had encoded both relevant aspects of the experiment (the domain and the frequencies).

@@

`r n.subj.cas.failed` participants were excluded from the analysis for failing to answer at least one of the attention check questions correctly, leaving a total of `r n.subj.cas-n.subj.cas.failed` responses for analysis.
The empirically elicited distributions of responses were not appreciably different for our two cover stories (herbs making animals sleepy, fertilizer making plants grow tall) and thus we collapse the data across these two stories.
The distributions that resulted from participants predicting the causal efficacy of the new substances are shown in Figure\ \@ref(fig:figure-causals)A.
<!-- \ndg{its unclear in figure caption whether those are emprical, predicted, or bda priors.} -->
As is visually apparent, the empirical prevalence distributions differ between conditions and nicely recapitulate the distributions supplied in the different experimental conditions, suggesting that the manipulation does indeed change participants' representations of what probabilities are likely to occur in each experimental condition. 
This diversity is important because the model of generalizations predicts differences in endorsement---for the same referent prevalence---depending on these priors.
<!-- \ndg{it'd be good to have some kid of stats here. maybe just show that empirical prealence distributions differ between conditions. also say how this matters: as before geeralization model predicts differences in endorsement for same target prevalence depending on priors.} -->
<!-- We hypothesize that with the distributions altered, endorsements of generalizations will similarly be affected. -->

@@

In this experiment, we tested whether the manipulated priors of Expt. 3A are causally related to the endorsement of causal statements.
Most of the experimental design was identical to that of Expt. 3A.

@@

The materials were the same as in Expt. 3A.

The first part of the experimental trial was the same as in Expt. 3A (the table of "previous experiments"; Figure \@ref(fig:causalExpt)A-C).
Upon continuing beyond the first part of the trial, the table of results and background story were removed from the screen and the participant is told that the results of the "lost experiment" were found (the experiment with a "?" in the table).^[
  We chose to have the scientists report on an earlier "lost experiment" to suggest a binomial generative process for the experiments wherein the scientists planned to perform 11 experiments, as opposed to alternative design wherein an 11th experiment is reported. Such a continuation of the series of experiments could imply a generative model following a geometric distribution where the scientists repeat the experiment until they reach one that is successful.
]
The results are reported to the participant in terms of how many out of 100 of the attempts were successful. 
Participants saw one of two reported frequencies: 20\% or 70\% (randomized between-subjects).
Participants were then asked to judge the causal sentence (e.g., "Herb X makes the animals sleepy") by either clicking "Yes" or "No" (Figure \@ref(fig:causalExpt)E). 
This allows us to test whether endorsement of a causal sentence for a given actual frequency is affected by the causal priors induced by our manipulation.
After responding, participants completed the same attention check as Expt. 3a.

@@

As predicted by our model, endorsements for a causal statement were sensitive to the referent prevalence of causal events and, critically, to the background distribution of other causes. 
When many other causes produced the effect very reliably (*common strong* condition), very few participants endorsed the causal statement for a causal frequency of 0.2, and were at chance when the causal frequency was 0.7 (Figure\ \@ref(fig:figure-causals), blue bars).
By contrast, when many other causes failed to produce the effect and those that did were not very reliable (*rare weak* condition; green in figure), at least half of participants endorsed the causal statement for a cause with causal prevalence of 0.2, and were at ceiling when the prevalence was 0.7.
The other two conditions (*rare deterministic* and *common weak*) led to endorsements intermediate between these two conditions.
These effects were predicted by our model with strong quantitative accuracy ($r^2(`r n.caus.endorse`) = `r r2.caus.rsa`$; MSE = $`r mse.caus.rsa`$).

@@

In our third case study, we applied our model to generalizations about causal events, without any changes.
In this domain, we successfully manipulated participants' beliefs about the expected prevalence of a causal relationship in a domain (Expt. 3A).
This was done using both unimodal (*common weak*, *common strong*) and bimodal (*rare weak*, *rare strong*) distributions. 
In Expt. 3B, we showed that these manipulated priors influenced endorsements of the corresponding causal statements.
In addition to further demonstrating the generality of this theory, these experiments show that the prevalence prior $P(p)$ is causally related to endorsements of generalizations in language.
<!-- To our knowledge, these are the first experiments to demonstrate how the prevalence of a feature among other categories can influence endorsing a generalization about a referent category. \ndg{fix last sentence. is this about geeralization? didn't our last experiments show this? is it about causation? huh?} -->

In these experiments, we used two cover stories that described plausible causal events: herbs making animals sleepy and fertilizers making plants grow tall.
<!-- \ndg{which reminds me: need to say something above (3a) about (no) differences between the cover stories?} -->
We chose these items because there was a plausible causal mechanism that could give rise to the property and these causal events could have ambiguous causal power associated with them (e.g., it is plausible that there are herbs that only weakly make animals sleepy and it is also plausible that there are herbs that almost deterministically make animals sleepy).
These two features of the domains make them particularly amenable to manipulation.
<!-- Inituive theories about these domains are flexible enough to permit such manipulations. -->
It is likely that other domain knowledge would interact with the experimentally-supplied "experimental data" to form a hybrid belief distribution.^[
If this were happening in our domains, we would expect this to show up in the results of Expt. 3A. Participants' predictions about the likely causal power of new causes would be expected to show a mixture of their abstract, intuitive theories and the experimentally supplied data.
]
For example, physical causal systems (e.g., billiard balls hitting each other) could strongly induce near-deterministic notions of causality, analogous to our *strong* priors conditions. 
Causal systems that demonstrate surprising or *a priori* unlikely effects (e.g., liquids melting concrete) could induce rarity about the existence of a non-zero causal power, analogous to our *rare* prior conditions. 
Our theory would predict that differences in endorsement in these cases would be mediated by differences in the corresponding prevalence prior distributions.
